Adaptive Sequential Model Selection

### 2015-05-05 paper.tex
forward stepwise definition

@@

\begin{proposition}[Regularized Likelihood Paths Satisfy SPSP]
  Model paths specified as in (\ref{eq:regPathDef_start}--\ref{eq:regPathDef_end}) satisfy the sub-path sufficiency principle.
\end{proposition}
\WFcomment{Actually, you just keep the times when the model changes... Need to recast notation a bit; indices of $\lambda$ (or $P$, here) need not match up with indices of model.}

@@

>>>>

\begin{model}[Generalized Sparse Model]\label{mod:genSparse}
  Let $M_\infty$ be a model parameterized by $\theta\in \Theta \sub \R^p$:
  \[
  M_{\infty} = \{F_\theta:\; \theta \in \Theta\}.
  \]
  For subsets $E\sub [p]$ define the model $M_E$ with active coefficients $E$ as follows:
  \[
  \Theta_E = \{\theta:\; \theta_j = 0, \;\;\forall j \notin E\}, 
  \quad M(E) = \{F_\theta:\; \theta\in \Theta_E\}.
  \]
\end{model}

In Model~\ref{mod:genSparse}, the {\em forward stepwise algorithm} proceeds as follows: we first set $E_0$ arbitrarily, then at step $k=1,\ldots,d$, we define
\begin{align}\label{eq:forwardDef_start}
j_k &= \argmax_j \max_{\theta\in\Theta_{E_{k-1}}} \ell(\theta; Y)\\
E_k &= E_{k-1} \cup \{j_k\}\\\label{eq:forwardDef_end}
M_k &= M(E_k)
\end{align}

\begin{proposition}[Forward Stepwise Satisfies SPSP]\label{prop:forwardSPSP}
  The forward stepwise algorithm defined in (\ref{eq:forwardDef_start}--\ref{eq:forwardDef_end}) satisfies the SPSP.
\end{proposition}
\begin{proof}
  \WFcomment{Write proof.}
\end{proof}

@@

\begin{proposition}[Regularized Likelihood Paths Satisfy SPSP]\label{prop:regPathSPSP}
  Model paths specified as in (\ref{eq:regPathDef_start}--\ref{eq:regPathDef_end}) satisfy the sub-path sufficiency principle.
\end{proposition}
\WFcomment{Actually, you just keep the times when the model changes... Need to recast notation a bit; indices of $\lambda$ (or $P$, here) need not match up with indices of model.}

@@

\section{Discussion}
